\forestclaw: Hybrid forest-of-octrees AMR for hyperbolic conservation laws

### 2013-07-30 docs/parco13/paper.tex
Rewrap to reduce the size of diff to abstract.tex
Copy some reviewer's comments

\alert{Review 2 requests more info on how this is done.  Sounds like they are more curious about the refinement overhead to other leaves on the tree and the strategy as to how refinement is decided.}

>>>>

\alert{Review 2 requests more info on how this is done.  Sounds like they are more curious about the refinement overhead to other leaves on the tree and the strategy as to how refinement is decided.
%
Quote: How is AMR working in detail. For example: Figure 1 shows a
2:1 refinement, thus refinement of a single patch could affect a whole region
of the computational domain. + The underlying equations are known to
Forestclaw: How is is the information shared with p4est (equation dependent
refinement criteria, refinement and coarsening strategies (interpolation,
integration).
}
